Transport map accelerated adaptive importance sampling, and application to inverse problems arising from multiscale stochastic reaction networks

### 2019-01-10 TETAIS.tex
Updated bib

\subsection{The chicken and egg paradox}
Another issue with the use of transport maps of this ilk, is that in
order to construct such a map, we require a representative sample from
the posterior distribution. Since these methods are designed to sample
from distributions which are inherently difficult to sample from, be
it due to multimodality, as looked at in \cite{cotter2015parallel}, or
as in this paper, due to the density being highly concentrated close
to a curved manifold in parameter space, it could be argued that accessing this initial set of
samples remains a hard problem. This remains an open problem, which we
are aiming to address in future work.

>>>>

% \subsection{The chicken and egg paradox}
% Another issue with the use of transport maps of this ilk, is that in
% order to construct such a map, we require a representative sample from
% the posterior distribution. Since these methods are designed to sample
% from distributions which are inherently difficult to sample from, be
% it due to multimodality, as looked at in \cite{cotter2015parallel}, or
% as in this paper, due to the density being highly concentrated close
% to a curved manifold in parameter space, it could be argued that accessing this initial set of
% samples remains a hard problem. This remains an open problem, which we
% are aiming to address in future work.
